---
title: "What this package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What this package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FALL224753dala0003)
```

# Introduction
This package contains functions used throughout the year.

## The first function
This function creates an n curve.
```{r}
FALL224753dala0003::myncurve(10,5)
```

## The second function
This function creates a histogram, given n and the number of iterations in a matrix.
```{r}
FALL224753dala0003::myclt(10, 10000)
```

## The third function
This function creates a histogram of a sample, given a specific quantitative variable in a given dataset
```{r}
library(Intro2R)
newObj <- FALL224753dala0003::myboot2(x=ddt$DDT)
newObj
```

## The fourth function
This function will generate the maximum likelihood estimates.
```{r}
FALL224753dala0003::mymaxlikg(theta=seq(0,1,length=10000))
```
